Effect of resonant and random excitation on the LHC beam in the context of pulsed hollow electron lens operation.

### 2018-02-16 resex.tex
Updated figures of measured current-density profiles

\subsection{Kicks in the central region (main solenoid)}
\label{core:sec:2}
For a perfectly annular and axially symmetric profile, the field in the region of the proton beam core vanishes as can be seen from Eq.~\ref{eq:field_2} and as illustrated in Fig.~\ref{fig:hel_field}. Fields at the location of the proton beam core thus only arise in case of profile imperfections of the electron beam, in particular if the axial symmetry is broken. Recently, the latest LHC hollow electron gun prototype was characterized at the Fermilab electron lens test stand \cite{hel_test_stand_fnal}. A typical measurement of the electron beam current density is shown in Fig.~\ref{core:fig:0}.
\begin{figure}[t]
		\centering
		\includegraphics[width=0.8\linewidth]{e-field-measured.png}
	\caption{Current density from measurements of the CHG1b hollow electron gun at the Fermilab electron lens test stand in 2017 \cite{hel_res_field_stancari_2017}. \textcolor{red}{Replace by 2D simulations - Giulio.}}
	\label{core:fig:0}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{CHG1b_170512_8p75A_2-4-2p7kG_500V_76mA_hires_Emap}
\includegraphics[width=\columnwidth]{CHG1b_170512_8p75A_2-4-2p7kG_500V_76mA_hires_Eslice}
\caption{Calculated relative electric field for the hollow electron
  gun in the transverse $x$-$y$ plane (left) and as 1-dimensional cuts
  through the $x$ and $y$ axes (right). The field calculations are
  based on measurements at the Fermilab electron-lens test stand
  combined with Warp calculations of the electric potentials and
  fields in a cylindrical beam pipe.}
\label{core:fig:1}
\end{figure}

>>>>

\subsection{Kicks in the central region (main solenoid)}
\label{core:sec:2}

\begin{figure*}
  \includegraphics[height=0.9\columnwidth]{CHG1b_170523_8p75A_2-4-2kG_500V_75mA_hires_2D} \hfill
  \includegraphics[height=0.9\columnwidth]{CHG1b_170523_8p75A_2-4-2kG_500V_75mA_hires_j-vs-r_binned_nogrid_nolabel}
  \caption{Example of current-density distribution measurements for
    the hollow electron gun prototype CHG1b, taken at the Fermilab
    electron lens test stand in
    2017~\cite{hel_res_field_stancari_2017}: 2-dimensional transverse
    profile measurement (left) and calculated 1-dimensional radial
    projection (right).}
  \label{core:fig:0}
\end{figure*}

\begin{figure*}
  \includegraphics[width=\columnwidth]{CHG1b_170512_8p75A_2-4-2p7kG_500V_76mA_hires_Emap} \hfill
  \includegraphics[width=\columnwidth]{CHG1b_170512_8p75A_2-4-2p7kG_500V_76mA_hires_Eslice}
  \caption{Calculated relative electric field for the hollow electron
    gun CHG1b in the transverse $x$-$y$ plane (left) and as
    1-dimensional cuts through the $x$ and $y$ axes (right). The field
    calculations are based on measurements at the Fermilab
    electron-lens test stand combined with Warp calculations of the
    electric potentials and fields in a cylindrical beam pipe.}
\label{core:fig:1}
\end{figure*}

For a perfectly annular and axially symmetric profile, the field in
the region of the proton beam core vanishes as can be seen from
Eq.~\ref{eq:field_2} and as illustrated in
Fig.~\ref{fig:hel_field}. Fields at the location of the proton beam
core thus only arise in case of profile imperfections of the electron
beam, in particular if the axial symmetry is broken. Recently, the
latest LHC hollow electron gun prototype was characterized at the
Fermilab electron lens test stand \cite{hel_test_stand_fnal}. A
typical measurement of the electron beam current density is shown in
Fig.~\ref{core:fig:0}.

@@
